IFC Inside: A General Approach to Retrofitting Languages with Dynamic Information Flow Control

### 2014-10-18 paper/real.tex
remove haskel

\begin{figure}
\centerline{\includegraphics[width=\columnwidth]{figs/node}}
\caption{\label{fig:node} Retrofitting Node.js JavaScript with IFC.
This example shows how our trusted monitor (left) is used to mediate
communication between two tasks for which IFC is enforced (right).}
\end{figure}
%
All IFC primitives are mediated by the trusted library code (executing
as the main Node.js context), which tracks the current label, messages,
etc.\ of each task.  An example for |send|/|recv| is shown in
Figure~\ref{fig:node}.
%While V8 provides a means for sharing any object between contexts (used
%by same-origin contexts in Blink),
Our system conservatively restricts
the kinds of messages that can be exchanged by tasks by
only allowing string values to be exchanged via |send| (and |sandbox|).
%
In our formalization, this amounts to restricting the IFC language rule
for |send| in the following way:
%{
\newcommand{\str}{"string"}
%format tOf (e) = "\texttt{typeOf}("e")\texttt{ === \str}"
%format ttrue = "\texttt{true}"
\begin{mathpar}
\inferrule[JS-send]
{
|il canFlowTo il'|\\
|iS(id') = Q|\\
|iS' = iS [ mapsto id' (il', id,  iv) , Q ]|\\
|ie = IT te|\\
|conf tS (tOf te) -> conf tS ttrue|
}
{|
iconf iS (fullconf id il tS (iniEi (send id' il' iv)), ldots)
.->
iS'; sched step (fullconf id il tS (iniEi unit), ldots)
|}
\end{mathpar}
%}
%
For convenience, we have implemented a library that provides
more flexible primitives, which, among other things,
automatically marshalls JSON objects to/from strings on each
|send|/|recv|.

@@

%% \subsection{Haskell}
%% \label{sec:real:hs}
%% Our work borrows ideas from a Haskell coarse-grained IFC
%% system called LIO~\cite{lio, stefan:addressing-covert}.
%% %
%% LIO relies on Haskell's strong type system and monadic encoding of
%% side-effecting computations to achieve isolation and define the IFC
%% sub-language.
%% %
%% Specifically LIO provides the \verb|LIO| monad as a way of restricting
%% (almost all) side-effects; this monad also keeps track of a current
%% label which is, in turn, used by trusted code when defining core IFC
%% functions, such as |getLabel|.
%% %
%% In the context of our framework, LIO can be understood as follows: the
%% \emph{pure subset} of Haskell is the target language, while the
%% monadic subset of Haskell, operating in the \verb|LIO| monad, is the
%% IFC language.

%% %Indeed, by rephrasing LIO in terms of our framework, we simplified
%% %LIO's treatment of exceptions.
%% %
%% LIO originally associated labels with exceptions, in a
%% similar style to fine-grained
%% systems~\cite{stefan:2012:arxiv-flexible, Hritcu:2013:YIB:2497621.2498098}.
%% %
%% In particular, the label of an exception was set to the current label
%% at the time of the throw, and used by a custom catch construct to
%% raise the current label, thereby preventing leaks due to exceptional
%% control flows.
%% %
%% In addition to being overly complex, the interaction of exceptions
%% with clearance (which sets an upper bound on the current label, see
%% Section~\ref{sec:clearance}) was incorrect: the clearance
%% was restored to the clearance at point of the catch (a consequence of
%% defining \verb|LIO| using a State monad).
%% %
%% Furthermore, pure exceptions (e.g., divide by zero) always percolated to
%% trusted code, effectively allowing for denial of service attacks.
%% %
%% The insights gained when viewing coarse-grained IFC as presented in this
%% paper led to a much cleaner, simpler treatment of exceptions in LIO,
%% which has now been adapted by LIO.
%% %By using isolated tasks, and thus treating the current label (and
%% %clearance) as global, the underlying Haskell exception system can be
%% %used directly: exceptional control flow does not affect IFC.

%% \subsection{C}
%% \label{sec:real:c}
%% %
%% C programs are able to execute arbitrary (machine) code, access
%% arbitrary memory, and perform arbitrary system calls.
%% %
%% Thus, the confinement of C programs must be imposed by the underlying OS
%% and hardware.
%% %
%% For instance, our notion of isolation can be achieved using Dune's
%% hardware protection mechanisms~\cite{Belay:2012:DSU:2387880.2387913},
%% similar to a simpler version of
%% Wedge~\cite{Belay:2012:DSU:2387880.2387913,
%% Bittau:2008:WSA:1387589.1387611} with an information flow control
%% policy.
%% %
%% Using page tables, a (trusted) IFC runtime could ensure that each task,
%% implemented as a lightweight process, can only access the memory it
%% allocates---tasks do not have access to any shared memory.
%% %
%% In addition, ring protection could be used to intercept system
%% calls performed by
%% a task and only permit those corresponding to our IFC language (such as
%% |getLabel| or |send|).
%% %
%% Dune's hardware protection mechanism would allow us to provide a concrete
%% implementation that is efficient and relatively simple to reason
%% about, but other sandboxing mechanisms could be used in place of Dune.

%% In this setting, the combined language of Section~\ref{sec:retrofit}
%% can be interpreted in the following way: calling from the target
%% language to the IFC language corresponds to invoking a system call.
%% %
%% Creating a new task with the |sandbox| system call corresponds to
%% \emph{forking} a process.  Using page tables we can ensure that
%% there will be no shared memory
%% (effectively
%% defining |ap klone tS
%% = tS0|, where |tS0| is the set of pages necessary to bootstrap a
%% lightweight process.)
%% %
%% Similarly, control over page tables and protection bits allows us to
%% define a |send| syscall that copies pages to our
%% (trusted) runtime queue; and, correspondingly, a |recv| that copies
%% the pages from the runtime queue to the (untrusted) receiver.
%% %
%% Since C is not memory safe, conditions on these system calls are
%% meaningless.
%% %
%% We leave the implementation of this IFC system for C to future work.

>>>>

\begin{figure}
\centerline{\includegraphics[width=0.7\columnwidth]{figs/node}}
\caption{\label{fig:node} Retrofitting Node.js JavaScript with IFC.
This example shows how our trusted monitor (left) is used to mediate
communication between two tasks for which IFC is enforced (right).}
\end{figure}
%
All IFC primitives are mediated by the trusted library code (executing
as the main Node.js context), which tracks the current label, messages,
etc.\ of each task.  An example for |send|/|recv| is shown in
Figure~\ref{fig:node}.
%While V8 provides a means for sharing any object between contexts (used
%by same-origin contexts in Blink),
Our system conservatively restricts
the kinds of messages that can be exchanged by tasks by
only allowing string values to be exchanged via |send| (and |sandbox|).
%
In our formalization, this amounts to restricting the IFC language rule
for |send| in the following way:
%{
\newcommand{\str}{"string"}
%format tOf (e) = "\texttt{typeOf}("e")\texttt{ === \str}"
%format ttrue = "\texttt{true}"
\begin{mathpar}
\inferrule[JS-send]
{
|il canFlowTo il'|\\
|iS(id') = Q|\\
|iS' = iS [ mapsto id' (il', id,  iv) , Q ]|\\
|ie = IT te|\\
|conf tS (tOf te) -> conf tS ttrue|
}
{|
iconf iS (fullconf id il tS (iniEi (send id' il' iv)), ldots)
.->
iS'; sched step (fullconf id il tS (iniEi unit), ldots)
|}
\end{mathpar}
%}
%
For convenience, we have implemented a library that provides
more flexible primitives, which, among other things,
automatically marshalls JSON objects to/from strings on each
|send|/|recv|.

@@

%\subsection{Haskell}
%\label{sec:real:hs}
%Our work borrows ideas from a Haskell coarse-grained IFC
%system called LIO~\cite{lio, stefan:addressing-covert}.
%%
%LIO relies on Haskell's strong type system and monadic encoding of
%side-effecting computations to achieve isolation and define the IFC
%sub-language.
%%
%Specifically LIO provides the \verb|LIO| monad as a way of restricting
%(almost all) side-effects; this monad also keeps track of a current
%label which is, in turn, used by trusted code when defining core IFC
%functions, such as |getLabel|.
%%
%In the context of our framework, LIO can be understood as follows: the
%\emph{pure subset} of Haskell is the target language, while the
%monadic subset of Haskell, operating in the \verb|LIO| monad, is the
%IFC language.
%
%%Indeed, by rephrasing LIO in terms of our framework, we simplified
%%LIO's treatment of exceptions.
%%
%LIO originally associated labels with exceptions, in a
%similar style to fine-grained
%systems~\cite{stefan:2012:arxiv-flexible, Hritcu:2013:YIB:2497621.2498098}.
%%
%In particular, the label of an exception was set to the current label
%at the time of the throw, and used by a custom catch construct to
%raise the current label, thereby preventing leaks due to exceptional
%control flows.
%%
%In addition to being overly complex, the interaction of exceptions
%with clearance (which sets an upper bound on the current label, see
%Section~\ref{sec:clearance}) was incorrect: the clearance
%was restored to the clearance at point of the catch (a consequence of
%defining \verb|LIO| using a State monad).
%%
%Furthermore, pure exceptions (e.g., divide by zero) always percolated to
%trusted code, effectively allowing for denial of service attacks.
%%
%The insights gained when viewing coarse-grained IFC as presented in this
%paper led to a much cleaner, simpler treatment of exceptions in LIO,
%which has now been adapted by LIO.
%%By using isolated tasks, and thus treating the current label (and
%%clearance) as global, the underlying Haskell exception system can be
%%used directly: exceptional control flow does not affect IFC.

\subsection{C}
\label{sec:real:c}
%
C programs are able to execute arbitrary (machine) code, access
arbitrary memory, and perform arbitrary system calls.
%
Thus, the confinement of C programs must be imposed by the underlying OS
and hardware.
%
For instance, our notion of isolation can be achieved using Dune's
hardware protection mechanisms~\cite{Belay:2012:DSU:2387880.2387913},
similar to a simpler version of
Wedge~\cite{Belay:2012:DSU:2387880.2387913,
Bittau:2008:WSA:1387589.1387611} with an information flow control
policy.
%
Using page tables, a (trusted) IFC runtime could ensure that each task,
implemented as a lightweight process, can only access the memory it
allocates---tasks do not have access to any shared memory.
%
In addition, ring protection could be used to intercept system
calls performed by
a task and only permit those corresponding to our IFC language (such as
|getLabel| or |send|).
%
Dune's hardware protection mechanism would allow us to provide a concrete
implementation that is efficient and relatively simple to reason
about, but other sandboxing mechanisms could be used in place of Dune.

In this setting, the combined language of Section~\ref{sec:retrofit}
can be interpreted in the following way: calling from the target
language to the IFC language corresponds to invoking a system call.
%
Creating a new task with the |sandbox| system call corresponds to
\emph{forking} a process.  Using page tables we can ensure that
there will be no shared memory
(effectively
defining |ap klone tS
= tS0|, where |tS0| is the set of pages necessary to bootstrap a
lightweight process.)
%
Similarly, control over page tables and protection bits allows us to
define a |send| syscall that copies pages to our
(trusted) runtime queue; and, correspondingly, a |recv| that copies
the pages from the runtime queue to the (untrusted) receiver.
%
Since C is not memory safe, conditions on these system calls are
meaningless.
%
We leave the implementation of this IFC system for C to future work.
